How accurate is CC4 for vertical excitation energies?

### 2021-05-03 Manuscript/CC4.tex
CC2 data

	\begin{tabular}{llrrrrrrrrrrrrrr}
				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{6}{c}{aug-cc-pVTZ}		\\	
				\cline{3-10} \cline{11-16}
	Mol.	&	State				&CCSD	&CC3	&CCSDT-3&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
									&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\

@@

	\ce{NH3}	&	$^1A_2$ 		&6.455	&6.464	&6.472	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
				&	$^1E$			&8.024	&8.061	&8.065	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
				&	$^1A_1$ 		&9.649	&9.664	&9.668	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
				&	$^1A_2$ 		&10.376	&10.396	&10.402	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
	\ce{BH}		&	$^1\Pi$ 		&2.970	&2.955	&2.958	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
	\ce{BF}		&	$^1\Pi$ 		&6.534	&6.478	&6.491	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
	\ce{CO}		&	$^1\Pi$ 		&8.671	&8.572	&8.591	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
				&	$^1\Sigma^-$ 	&10.096	&10.122	&10.112	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
				&	$^1\Delta$ 		&10.210	&10.225	&10.220	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
				&	$^1\Sigma^+$ 	&11.171	&10.917	&10.989	&10.944	&10.925	&10.926	&10.919	&			&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
				&	$^1\Sigma^+$ 	&11.710	&11.483	&11.543	&11.518	&11.510	&11.510	&11.506	&			&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
				&	$^1\Pi$ 		&11.973	&11.737	&11.802	&11.767	&11.757	&11.758	&11.753	&			&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
	\ce{N2}		&	$^1\Pi_g$  		&9.495	&9.442	&9.450	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
				&	$^1\Sigma_u^-$	&10.197	&10.059	&10.063	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
				&	$^1\Delta_u$ 	&10.607	&10.433	&10.449	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
				&	$^1\Sigma_g^+$	&13.326	&13.229	&13.270	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
				&	$^1\Pi_u$  		&13.451	&13.279	&13.323	&13.174	&13.128	&13.131	&13.127	&			&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
				&	$^1\Sigma_u^+$	&13.250	&13.146	&13.186	&13.130	&13.099	&13.109	&13.107	&			&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
				&	$^1\Pi_u$ 		&13.765	&13.635	&13.663	&13.591	&13.551	&13.560	&13.558	&			&13.674	&13.494	&13.455	&13.409	&13.419\\
	\ce{HCl}	&	$^1\Pi$ 		&7.862	&7.819	&7.828	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
	\ce{H2S}	&	$^1B_1$  		&6.141	&6.098	&6.110	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
				&	$^1A_2$  		&6.343	&6.293	&6.299	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
	\ce{H2O}	&	$^1B_1$  		&7.447	&7.511	&7.510	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
				&	$^1A_2$  		&9.213	&9.293	&9.291	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
				&	$^1A_1$  		&9.861	&9.921	&9.919	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\

@@

	MAE			&					&0.112	&0.041	&0.028	&0.018	&0.003	&0.002	\\
	MSE			&					&0.079	&0.032	&0.014	&0.002	&0.000	&0.000	\\

@@

Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates.

>>>>

	\begin{tabular}{llrrrrrrrrrrrrrrr}
				&		&	\mc{8}{c}{aug-cc-pVDZ}		&		\mc{7}{c}{aug-cc-pVTZ}		\\	
				\cline{3-10} \cline{11-17}
	Mol.	&	State				&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&CCSDTQP	&FCI	
									&CC2	&CCSD	&CC3	&CCSDT	&CC4	&CCSDTQ	&FCI			\\

@@

	\ce{NH3}	&	$^1A_2$ 		&6.249	&6.455	&6.464	&6.462	&6.479	&6.480	&6.482	&6.483(1)	&6.387	&6.600	&6.573	&6.571	&6.585	&6.586	&6.593(22)	\\	
				&	$^1E$			&7.733	&8.024	&8.061	&8.057	&8.078	&8.079	&8.081	&8.082(1)	&7.847	&8.148	&8.146	&8.143	&8.161	&8.161	&8.171(20)	\\	
				&	$^1A_1$ 		&9.400	&9.649	&9.664	&9.659	&9.677	&9.677	&9.680	&9.681(8)	&9.051	&9.334	&9.318	&9.314	&9.331	&9.331	&9.340(19)	\\
				&	$^1A_2$ 		&10.148	&10.376	&10.396	&10.391	&10.409	&10.409	&10.411	&10.412(1)	&9.654	&9.953	&9.945	&9.939	&9.957	&9.957	&9.967(19)	\\
	\ce{BH}		&	$^1\Pi$ 		&2.862	&2.970	&2.955	&2.946	&2.947	&2.947	&2.947	&2.947(0)	&2.831	&2.928	&2.910	&2.900	&2.901	&2.901	&2.901(0)	\\
	\ce{BF}		&	$^1\Pi$ 		&6.509	&6.534	&6.478	&6.491	&6.484	&6.485	&6.485	&6.485(1)	&6.445	&6.464	&6.410	&6.423	&6.416	&6.417	&6.418(2)\\
	\ce{CO}		&	$^1\Pi$ 		&8.724	&8.671	&8.572	&8.574	&8.562	&8.563	&8.561	&8.565(2)	&8.638	&8.587	&8.486	&8.492	&8.479	&8.480	&	\\
				&	$^1\Sigma^-$ 	&10.381	&10.096	&10.122	&10.062	&10.055	&10.057	&10.057	&10.056(1)	&10.297	&9.986	&9.992	&9.940	&9.930	&9.932	&	\\
				&	$^1\Delta$ 		&10.685	&10.210	&10.225	&10.178	&10.167	&10.169	&10.168	&10.168(1)	&10.604	&10.123	&10.119	&10.076	&10.064	&10.066	&	\\
				&	$^1\Sigma^+$ 	&11.089	&11.171	&10.917	&10.944	&10.925	&10.926	&10.919	&			&11.106	&11.222	&10.943	&10.987	&10.961	&10.963	&	\\
				&	$^1\Sigma^+$ 	&11.628	&11.710	&11.483	&11.518	&11.510	&11.510	&11.506	&			&11.626	&11.751	&11.489	&11.540	&11.521	&11.523	&	\\
				&	$^1\Pi$ 		&11.878	&11.973	&11.737	&11.767	&11.757	&11.758	&11.753	&			&11.825	&11.960	&11.690	&11.737	&11.719	&11.720	&	\\
	\ce{N2}		&	$^1\Pi_g$  		&9,528	&9.495	&9.442	&9.417	&9.409	&9.411	&9.409	&9.411(3)	&9.439	&9.408	&9.344	&9.326	&9.317	&9.319	&	\\
				&	$^1\Sigma_u^-$	&10.428	&10.197	&10.059	&10.060	&10.063	&10.055	&10.054	&10.054(0)	&10.320	&9.996	&9.885	&9.890	&9.883	&9.878	&9.879(4)\\
				&	$^1\Delta_u$ 	&10.961	&10.607	&10.433	&10.436	&10.439	&10.430	&10.428	&10.429(0)	&10.863	&10.443	&10.293	&10.302	&10.294	&10.287	&10.289(12)\\
				&	$^1\Sigma_g^+$	&13.077	&13.326	&13.229	&13.202	&13.171	&13.182	&13.181	&13.180(1)	&12.833	&13.151	&13.013	&12.999	&12.962	&12.974	&	\\
				&	$^1\Pi_u$  		&13.309	&13.451	&13.279	&13.174	&13.128	&13.131	&13.127	&			&13.152	&13.422	&13.223	&13.140	&13.091	&13,095	&	\\
				&	$^1\Sigma_u^+$	&12.937	&13.250	&13.146	&13.130	&13.099	&13.109	&13.107	&			&12.888	&13.263	&13.120	&13.118	&13.078	&13.090	&	\\
				&	$^1\Pi_u$ 		&14.091	&13.765	&13.635	&13.591	&13.551	&13.560	&13.558	&			&13.963	&13.674	&13.494	&13.455	&13.409	&13.419\\
	\ce{HCl}	&	$^1\Pi$ 		&7.895	&7.862	&7.819	&7.815	&7.822	&7.822	&7.823	&7.823(0)	&7.959	&7.906	&7.840	&7.834	&7.837	&7.837	&7.838(1)\\
	\ce{H2S}	&	$^1B_1$  		&6.157	&6.141	&6.098	&6.098	&6.102	&6.103	&6.103	&6.103(1)	&6.304	&6.294	&6.240	&6.237	&6.238	&6.238	&6.240(7)\\
				&	$^1A_2$  		&6.431	&6.343	&6.293	&6.286	&6.286	&6.286	&6.286	&6.286(0)	&6.345	&6.246	&6.192	&6.185	&6.181	&6.181	&6.181(6) \\
	\ce{H2O}	&	$^1B_1$  		&7.089	&7.447	&7.511	&7.497	&7.531	&7.528	&7.532	&7.533(0)	&7.234	&7.597	&7.605	&7.591	&7.623	&7.620	&7.626(3)\\
				&	$^1A_2$  		&8.743	&9.213	&9.293	&9.279	&9.317	&9.313	&9.318	&9.318(0)	&8.889	&9.361	&9.382	&9.368	&9.405	&9.400	&9.407(7)\\
				&	$^1A_1$  		&9.486	&9.861	&9.921	&9.903	&9.940	&9.937	&9.941	&9.941(0)	&9.580	&9.957	&9.966	&9.949	&9.986	&9.981	&9.986(2)\\

@@

	MAE			&					&0.257	&0.112	&0.028	&0.018	&0.003	&0.002	\\
	MSE			&					&0.031	&0.079	&0.014	&0.002	&0.000	&0.000	\\

@@

Table \ref{tab:BigTab} gathers vertical excitation energies obtained with various CC models as well as FCI estimates for the two basis sets as well as the mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP for these models.
